A Logistic Regression Prediction of 2024 Election Odds Gives VP Harris a 38.3% Winrate

### 2024-11-04 paper/paper.qmd
really reallyreally last thing i forgot aaaaaa

# aggregated dataset for summary statistics
# datasets with lower numeric scores already includes polls with a score of 3.0
all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
    biden_2020, trump_2020)

```

@@

ggplot(all_combined, aes(x = pct)) +
  geom_histogram(
    binwidth = 1,                # Adjust bin width for granularity
    fill = "#2c7bb6",            # Aesthetic fill color (steel blue)
    color = "white",             # Border color for bins
    alpha = 0.8                   # Transparency of the fill
  ) +
  labs(
    x = "Percentage Support",
    y = "Number of Polls"
  ) +
  theme_minimal(base_size = 14) +   # Minimal theme with increased base font size
  theme(
    plot.title = element_text(
      size = 16, 
      face = "bold", 
      hjust = 0.5,                # Center the title
      margin = margin(b = 10)     # Add space below the title
    ),
    plot.subtitle = element_text(
      size = 12, 
      hjust = 0.5, 
      margin = margin(b = 20)     # Add space below the subtitle
    ),
    axis.title = element_text(face = "bold"), # Bold axis titles
    axis.text = element_text(color = "gray30"), # Dark gray axis text
    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
    panel.grid.minor = element_blank()                 # Remove minor grid lines
  ) +
  # Add a vertical line for the mean percentage support
  geom_vline(
    aes(xintercept = mean(pct, na.rm = TRUE)),
    color = "#d73027",           # Aesthetic color (red)
    linetype = "dashed", 
    size = 1
  ) +
  # Annotate the mean value on the plot
  annotate(
    "text",
    x = mean(all_combined$pct, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
    y = Inf,                                     # Position text at the top of the plot
    label = paste("Mean:", round(mean(all_combined$pct, na.rm = TRUE), 1), "%"),
    vjust = 2,                                   # Vertical adjustment
    color = "#d73027",
    size = 5,
    fontface = "bold"
  )

```

@@

ggplot(all_combined %>% filter(cycle == 2020), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```
\vspace{1em}
\FloatBarrier

@@

ggplot(all_combined %>% filter(cycle == 2024), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```
\FloatBarrier
The end date indicates the date that a poll ends on. The dates are graphed separately between the 2020 and 2024 cycles for ease of viewing. Notice how there is a disproportionately large uptick in the number of polls that end on the end of a month.

@@

ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0,1), labels = c("No Sponsor", "Has Sponsor")))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Has Sponsor",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

@@

ggplot(all_combined, aes(x = factor(transparency_score))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Transparency Score",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

@@

ggplot(all_combined, aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Sample Size",
    y = "Number of Polls"
  ) +
  scale_x_continuous(labels = scales::comma) +
  coord_cartesian(xlim = c(0, 6000)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

@@

combined_Pennsylvania <- full_join(
  trump_Pennsylvania,
  harris_Pennsylvania,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Georgia <- full_join(
  trump_Georgia,
  harris_Georgia,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_North_Carolina <- full_join(
  trump_North_Carolina,
  harris_North_Carolina,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Michigan <- full_join(
  trump_Michigan,
  harris_Michigan,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Arizona <- full_join(
  trump_Arizona,
  harris_Arizona,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Wisconsin <- full_join(
  trump_Wisconsin,
  harris_Wisconsin,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Nevada <- full_join(
  trump_Nevada,
  harris_Nevada,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

@@

combined_Pennsylvania <- combined_Pennsylvania %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Pennsylvania, type = "response"), 2)
  )

roc_obj_Pennsylvania <- roc(combined_Pennsylvania$harris_win,
                  combined_Pennsylvania$harris_win_prob)

@@

combined_Georgia <- combined_Georgia %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Georgia, type = "response"), 2)
  )

roc_obj_Georgia <- roc(combined_Georgia$harris_win,
                            combined_Georgia$harris_win_prob)

@@

combined_North_Carolina <- combined_North_Carolina %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_North_Carolina, type = "response"), 2)
  )

roc_obj_North_Carolina <- roc(combined_North_Carolina$harris_win,
                            combined_North_Carolina$harris_win_prob)

@@

combined_Michigan <- combined_Michigan %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Michigan, type = "response"), 2)
  )

roc_obj_Michigan <- roc(combined_Michigan$harris_win,
                            combined_Michigan$harris_win_prob)

@@

combined_Arizona <- combined_Arizona %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Arizona, type = "response"), 2)
  )

roc_obj_Arizona <- roc(combined_Arizona$harris_win,
                            combined_Arizona$harris_win_prob)

@@

combined_Wisconsin <- combined_Wisconsin %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Wisconsin, type = "response"), 2)
  )

roc_obj_Wisconsin <- roc(combined_Wisconsin$harris_win,
                            combined_Wisconsin$harris_win_prob)

@@

combined_Nevada <- combined_Nevada %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Nevada, type = "response"), 2)
  )

roc_obj_Nevada <- roc(combined_Nevada$harris_win,
                            combined_Nevada$harris_win_prob)

auc_value_Nevada <- auc(roc_obj_Nevada)

```

@@

# model adjusted support percentage by time and control variables
# first split training and testing dataset using an 80/20 split
set.seed(11451)
trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj, 
                                        p = 0.8, list = FALSE)
data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
data_test_trump_adj  <- trump_2024_national_adj[-trainIndex_trump_adj, ]

trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj, 
                                         p = 0.8, list = FALSE)
data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
data_test_harris_adj  <- harris_2024_national_adj[-trainIndex_harris_adj, ]

@@

# repeat for unadjusted support levels
trainIndex_trump <- createDataPartition(trump_2024_national$pct, 
                                        p = 0.8, list = FALSE)
data_train_trump <- trump_2024_national[trainIndex_trump, ]
data_test_trump  <- trump_2024_national[-trainIndex_trump, ]

trainIndex_harris <- createDataPartition(harris_2024_national$pct, 
                                         p = 0.8, list = FALSE)
data_train_harris <- harris_2024_national[trainIndex_harris, ]
data_test_harris  <- harris_2024_national[-trainIndex_harris, ]

@@

combined_national <- full_join(
  trump_2024_national,
  harris_2024_national,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

@@

# repeat for adjusted support levels
combined_national_adj <- full_join(
  trump_2024_national_adj,
  harris_2024_national_adj,
  by = c("pollster", "has_sponsor", "pollscore",
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

@@

# include predicted outcomes to the dataframes
combined_national <- combined_national %>%
  mutate(
    harris_win_prob = round(100*predict(model_logistic, type = "response"), 2)
  )

combined_national_adj <- combined_national_adj %>%
  mutate(
    harris_win_prob = round(100*predict(model_logistic_adj, 
                                        type = "response"), 2)
  )

@@

# ROC Curve and AUC
roc_obj <- roc(combined_national$harris_win,
               combined_national$harris_win_prob)
auc_value <- auc(roc_obj)

roc_obj_adj <- roc(combined_national_adj$harris_win,
               combined_national_adj$harris_win_prob)
auc_value_adj <- auc(roc_obj_adj)
```
For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization. Their respective ROC plots are presented as @fig-log and @fig-logadj.

@@

#### Results ####
# To predict the outcome on election day, generate 1000 hypothetical data points
# using the election day as end_date and the normal curve of other input 
# variables, mimicing all the situations that may happen on election day
hypothetical_data_Pennsylvania <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Pennsylvania$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Pennsylvania$transparency_score), 
                             sd = sd(combined_Pennsylvania$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Pennsylvania$sample_size),
                      sd = sd(combined_Pennsylvania$sample_size))
)

hypothetical_data_Georgia <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Georgia$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Georgia$transparency_score), 
                             sd = sd(combined_Georgia$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Georgia$sample_size),
                      sd = sd(combined_Georgia$sample_size))
)

hypothetical_data_North_Carolina <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_North_Carolina$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_North_Carolina$transparency_score), 
                             sd = sd(combined_North_Carolina$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_North_Carolina$sample_size),
                      sd = sd(combined_North_Carolina$sample_size))
)

hypothetical_data_Michigan <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Michigan$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Michigan$transparency_score), 
                             sd = sd(combined_Michigan$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Michigan$sample_size),
                      sd = sd(combined_Michigan$sample_size))
)

hypothetical_data_Arizona <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Arizona$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Arizona$transparency_score), 
                             sd = sd(combined_Arizona$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Arizona$sample_size),
                      sd = sd(combined_Arizona$sample_size))
)

hypothetical_data_Wisconsin <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Wisconsin$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Wisconsin$transparency_score), 
                             sd = sd(combined_Wisconsin$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Wisconsin$sample_size),
                      sd = sd(combined_Wisconsin$sample_size))
)

hypothetical_data_Nevada <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Nevada$has_sponsor)),
  transparency_score = rnorm(1000, mean = mean(combined_Nevada$transparency_score), 
                             sd = sd(combined_Nevada$transparency_score)),
  sample_size = rnorm(1000, mean = mean(combined_Nevada$sample_size),
                      sd = sd(combined_Nevada$sample_size))
)

# run the corresponding logistic regression on the hypothetical data of each
# state and average the outcomes to find the expected win rate of Harris
# on election day
hypothetical_data_Pennsylvania <- hypothetical_data_Pennsylvania %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
  )

hypothetical_data_Georgia <- hypothetical_data_Georgia %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Georgia, newdata = ., type = "response"), 2)
  )

hypothetical_data_North_Carolina <- hypothetical_data_North_Carolina %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
  )

hypothetical_data_Michigan <- hypothetical_data_Michigan %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Michigan, newdata = ., type = "response"), 2)
  )

hypothetical_data_Arizona <- hypothetical_data_Arizona %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Arizona, newdata = ., type = "response"), 2)
  )

hypothetical_data_Wisconsin <- hypothetical_data_Wisconsin %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
  )

hypothetical_data_Nevada <- hypothetical_data_Nevada %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Nevada, newdata = ., type = "response"), 2)
  )

@@

# Function to calculate probability of a specific combination
calc_combo_prob <- function(combo, states) {
  prob <- 1
  for(i in 1:nrow(states)) {
    if(i %in% combo) {
      prob <- prob * states$prob[i]
    } else {
      prob <- prob * (1 - states$prob[i])
    }
  }
  return(prob)
}

@@

# Check each possible combination
for(i in 1:(2^n_states - 1)) {
  # Convert number to binary to get combination
  combo <- which(intToBits(i)[1:n_states] == 1)

@@

  # If this combination has enough votes, add its probability
  if(votes >= 44) {
    prob <- calc_combo_prob(combo, states)
    total_prob <- total_prob + prob
  }
}

# Trump
# Create data frame of states
states <- data.frame(
  state = c("PA", "GA", "NC", "MI", "WI", "NV","AZ"),
  prob = c(1-0.5551, 1-0.6801, 1-0.1033, 1-0.5151, 1-0.3792, 1-0.7679, 1-0), # Using 1-p for Trump's probabilities
  votes = c(20, 16, 15, 16, 10, 6, 11)
)

# Function to calculate probability of a specific combination
calc_combo_prob <- function(combo, states) {
  prob <- 1
  for(i in 1:nrow(states)) {
    if(i %in% combo) {
      prob <- prob * states$prob[i]
    } else {
      prob <- prob * (1 - states$prob[i])
    }
  }
  return(prob)
}

@@

  # If this combination has enough votes, add its probability
  if(votes >= 51) {
    prob <- calc_combo_prob(combo, states)
    total_prob <- total_prob + prob
  }
}

```

@@

plot(roc_obj_Pennsylvania)

```

@@

plot(roc_obj_Georgia)

```

@@

plot(roc_obj_North_Carolina)

```

@@

plot(roc_obj_Michigan)

```

@@

plot(roc_obj_Arizona)

```

@@

plot(roc_obj_Wisconsin)

```

@@

plot(roc_obj_Nevada)

```

@@

plot(roc_obj)

```

@@

plot(roc_obj)

>>>>

# aggregated dataset for summary statistics
# datasets with lower numeric scores already includes polls with a score of 3.0
all_combined <- bind_rows(
  harris_2024_lower, trump_2024_lower,
  biden_2020, trump_2020
)
```

@@

ggplot(all_combined, aes(x = pct)) +
  geom_histogram(
    binwidth = 1, # Adjust bin width for granularity
    fill = "#2c7bb6", # Aesthetic fill color (steel blue)
    color = "white", # Border color for bins
    alpha = 0.8 # Transparency of the fill
  ) +
  labs(
    x = "Percentage Support",
    y = "Number of Polls"
  ) +
  theme_minimal(base_size = 14) + # Minimal theme with increased base font size
  theme(
    plot.title = element_text(
      size = 16,
      face = "bold",
      hjust = 0.5, # Center the title
      margin = margin(b = 10) # Add space below the title
    ),
    plot.subtitle = element_text(
      size = 12,
      hjust = 0.5,
      margin = margin(b = 20) # Add space below the subtitle
    ),
    axis.title = element_text(face = "bold"), # Bold axis titles
    axis.text = element_text(color = "gray30"), # Dark gray axis text
    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
    panel.grid.minor = element_blank() # Remove minor grid lines
  ) +
  # Add a vertical line for the mean percentage support
  geom_vline(
    aes(xintercept = mean(pct, na.rm = TRUE)),
    color = "#d73027", # Aesthetic color (red)
    linetype = "dashed",
    size = 1
  ) +
  # Annotate the mean value on the plot
  annotate(
    "text",
    x = mean(all_combined$pct, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
    y = Inf, # Position text at the top of the plot
    label = paste("Mean:", round(mean(all_combined$pct, na.rm = TRUE), 1), "%"),
    vjust = 2, # Vertical adjustment
    color = "#d73027",
    size = 5,
    fontface = "bold"
  )
```

@@

ggplot(all_combined %>% filter(cycle == 2020), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```
\vspace{1em}
\FloatBarrier

@@

ggplot(all_combined %>% filter(cycle == 2024), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```
\FloatBarrier
The end date indicates the date that a poll ends on. The dates are graphed separately between the 2020 and 2024 cycles for ease of viewing. Notice how there is a disproportionately large uptick in the number of polls that end on the end of a month.

@@

ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0, 1), labels = c("No Sponsor", "Has Sponsor")))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Has Sponsor",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )
```

@@

ggplot(all_combined, aes(x = factor(transparency_score))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Transparency Score",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )
```

@@

ggplot(all_combined, aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Sample Size",
    y = "Number of Polls"
  ) +
  scale_x_continuous(labels = scales::comma) +
  coord_cartesian(xlim = c(0, 6000)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )
```

@@

combined_Pennsylvania <- full_join(
  trump_Pennsylvania,
  harris_Pennsylvania,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_Georgia <- full_join(
  trump_Georgia,
  harris_Georgia,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_North_Carolina <- full_join(
  trump_North_Carolina,
  harris_North_Carolina,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_Michigan <- full_join(
  trump_Michigan,
  harris_Michigan,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_Arizona <- full_join(
  trump_Arizona,
  harris_Arizona,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_Wisconsin <- full_join(
  trump_Wisconsin,
  harris_Wisconsin,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

combined_Nevada <- full_join(
  trump_Nevada,
  harris_Nevada,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

@@

combined_Pennsylvania <- combined_Pennsylvania %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Pennsylvania, type = "response"), 2)
  )

roc_obj_Pennsylvania <- roc(
  combined_Pennsylvania$harris_win,
  combined_Pennsylvania$harris_win_prob
)

@@

combined_Georgia <- combined_Georgia %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Georgia, type = "response"), 2)
  )

roc_obj_Georgia <- roc(
  combined_Georgia$harris_win,
  combined_Georgia$harris_win_prob
)

@@

combined_North_Carolina <- combined_North_Carolina %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_North_Carolina, type = "response"), 2)
  )

roc_obj_North_Carolina <- roc(
  combined_North_Carolina$harris_win,
  combined_North_Carolina$harris_win_prob
)

@@

combined_Michigan <- combined_Michigan %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Michigan, type = "response"), 2)
  )

roc_obj_Michigan <- roc(
  combined_Michigan$harris_win,
  combined_Michigan$harris_win_prob
)

@@

combined_Arizona <- combined_Arizona %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Arizona, type = "response"), 2)
  )

roc_obj_Arizona <- roc(
  combined_Arizona$harris_win,
  combined_Arizona$harris_win_prob
)

@@

combined_Wisconsin <- combined_Wisconsin %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Wisconsin, type = "response"), 2)
  )

roc_obj_Wisconsin <- roc(
  combined_Wisconsin$harris_win,
  combined_Wisconsin$harris_win_prob
)

@@

combined_Nevada <- combined_Nevada %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Nevada, type = "response"), 2)
  )

roc_obj_Nevada <- roc(
  combined_Nevada$harris_win,
  combined_Nevada$harris_win_prob
)

auc_value_Nevada <- auc(roc_obj_Nevada)
```

@@

# model adjusted support percentage by time and control variables
# first split training and testing dataset using an 80/20 split
set.seed(11451)
trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj,
  p = 0.8, list = FALSE
)
data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
data_test_trump_adj <- trump_2024_national_adj[-trainIndex_trump_adj, ]

trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj,
  p = 0.8, list = FALSE
)
data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
data_test_harris_adj <- harris_2024_national_adj[-trainIndex_harris_adj, ]

@@

# repeat for unadjusted support levels
trainIndex_trump <- createDataPartition(trump_2024_national$pct,
  p = 0.8, list = FALSE
)
data_train_trump <- trump_2024_national[trainIndex_trump, ]
data_test_trump <- trump_2024_national[-trainIndex_trump, ]

trainIndex_harris <- createDataPartition(harris_2024_national$pct,
  p = 0.8, list = FALSE
)
data_train_harris <- harris_2024_national[trainIndex_harris, ]
data_test_harris <- harris_2024_national[-trainIndex_harris, ]

@@

combined_national <- full_join(
  trump_2024_national,
  harris_2024_national,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

@@

# repeat for adjusted support levels
combined_national_adj <- full_join(
  trump_2024_national_adj,
  harris_2024_national_adj,
  by = c(
    "pollster", "has_sponsor", "pollscore",
    "transparency_score", "sample_size", "end_date", "state", "cycle"
  )
)

@@

# include predicted outcomes to the dataframes
combined_national <- combined_national %>%
  mutate(
    harris_win_prob = round(100 * predict(model_logistic, type = "response"), 2)
  )

combined_national_adj <- combined_national_adj %>%
  mutate(
    harris_win_prob = round(100 * predict(model_logistic_adj,
      type = "response"
    ), 2)
  )

@@

# ROC Curve and AUC
roc_obj <- roc(
  combined_national$harris_win,
  combined_national$harris_win_prob
)
auc_value <- auc(roc_obj)

roc_obj_adj <- roc(
  combined_national_adj$harris_win,
  combined_national_adj$harris_win_prob
)
auc_value_adj <- auc(roc_obj_adj)
```
For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization. Their respective ROC plots are presented as @fig-log and @fig-logadj.

@@

#### Results ####
# To predict the outcome on election day, generate 1000 hypothetical data points
# using the election day as end_date and the normal curve of other input
# variables, mimicing all the situations that may happen on election day
hypothetical_data_Pennsylvania <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Pennsylvania$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Pennsylvania$transparency_score),
    sd = sd(combined_Pennsylvania$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Pennsylvania$sample_size),
    sd = sd(combined_Pennsylvania$sample_size)
  )
)

hypothetical_data_Georgia <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Georgia$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Georgia$transparency_score),
    sd = sd(combined_Georgia$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Georgia$sample_size),
    sd = sd(combined_Georgia$sample_size)
  )
)

hypothetical_data_North_Carolina <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_North_Carolina$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_North_Carolina$transparency_score),
    sd = sd(combined_North_Carolina$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_North_Carolina$sample_size),
    sd = sd(combined_North_Carolina$sample_size)
  )
)

hypothetical_data_Michigan <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Michigan$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Michigan$transparency_score),
    sd = sd(combined_Michigan$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Michigan$sample_size),
    sd = sd(combined_Michigan$sample_size)
  )
)

hypothetical_data_Arizona <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Arizona$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Arizona$transparency_score),
    sd = sd(combined_Arizona$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Arizona$sample_size),
    sd = sd(combined_Arizona$sample_size)
  )
)

hypothetical_data_Wisconsin <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Wisconsin$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Wisconsin$transparency_score),
    sd = sd(combined_Wisconsin$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Wisconsin$sample_size),
    sd = sd(combined_Wisconsin$sample_size)
  )
)

hypothetical_data_Nevada <- tibble(
  end_date = as.Date("2024-11-05"),
  has_sponsor = rbinom(1000, size = 1, prob = mean(combined_Nevada$has_sponsor)),
  transparency_score = rnorm(1000,
    mean = mean(combined_Nevada$transparency_score),
    sd = sd(combined_Nevada$transparency_score)
  ),
  sample_size = rnorm(1000,
    mean = mean(combined_Nevada$sample_size),
    sd = sd(combined_Nevada$sample_size)
  )
)

# run the corresponding logistic regression on the hypothetical data of each
# state and average the outcomes to find the expected win rate of Harris
# on election day
hypothetical_data_Pennsylvania <- hypothetical_data_Pennsylvania %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Pennsylvania, newdata = ., type = "response"), 2)
  )

hypothetical_data_Georgia <- hypothetical_data_Georgia %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Georgia, newdata = ., type = "response"), 2)
  )

hypothetical_data_North_Carolina <- hypothetical_data_North_Carolina %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_North_Carolina, newdata = ., type = "response"), 2)
  )

hypothetical_data_Michigan <- hypothetical_data_Michigan %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Michigan, newdata = ., type = "response"), 2)
  )

hypothetical_data_Arizona <- hypothetical_data_Arizona %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Arizona, newdata = ., type = "response"), 2)
  )

hypothetical_data_Wisconsin <- hypothetical_data_Wisconsin %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Wisconsin, newdata = ., type = "response"), 2)
  )

hypothetical_data_Nevada <- hypothetical_data_Nevada %>%
  mutate(
    harris_win_prob = round(100 * predict(logistic_Nevada, newdata = ., type = "response"), 2)
  )

@@

# Function to calculate probability of a specific combination
calc_combo_prob <- function(combo, states) {
  prob <- 1
  for (i in 1:nrow(states)) {
    if (i %in% combo) {
      prob <- prob * states$prob[i]
    } else {
      prob <- prob * (1 - states$prob[i])
    }
  }
  return(prob)
}

@@

# Check each possible combination
for (i in 1:(2^n_states - 1)) {
  # Convert number to binary to get combination
  combo <- which(intToBits(i)[1:n_states] == 1)

@@

  # If this combination has enough votes, add its probability
  if (votes >= 44) {
    prob <- calc_combo_prob(combo, states)
    total_prob <- total_prob + prob
  }
}

# Trump
# Create data frame of states
states <- data.frame(
  state = c("PA", "GA", "NC", "MI", "WI", "NV", "AZ"),
  prob = c(1 - 0.5551, 1 - 0.6801, 1 - 0.1033, 1 - 0.5151, 1 - 0.3792, 1 - 0.7679, 1 - 0), # Using 1-p for Trump's probabilities
  votes = c(20, 16, 15, 16, 10, 6, 11)
)

# Function to calculate probability of a specific combination
calc_combo_prob <- function(combo, states) {
  prob <- 1
  for (i in 1:nrow(states)) {
    if (i %in% combo) {
      prob <- prob * states$prob[i]
    } else {
      prob <- prob * (1 - states$prob[i])
    }
  }
  return(prob)
}

@@

  # If this combination has enough votes, add its probability
  if (votes >= 51) {
    prob <- calc_combo_prob(combo, states)
    total_prob <- total_prob + prob
  }
}
```

@@

plot(roc_obj_Pennsylvania)
```

@@

plot(roc_obj_Georgia)
```

@@

plot(roc_obj_North_Carolina)
```

@@

plot(roc_obj_Michigan)
```

@@

plot(roc_obj_Arizona)
```

@@

plot(roc_obj_Wisconsin)
```

@@

plot(roc_obj_Nevada)
```

@@

plot(roc_obj)
```

@@

plot(roc_obj)
```
\FloatBarrier
